%\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}
{\parindent 0pt
I would like to take this opportunity to express my deep gratitude to my supervisor Dr. Hong Wei for offering me the opportunity to conduct this research and providing invaluable guidance and support. I am also in debt to my second supervisor Dr. James Ferryman for all the helpful suggestions and support.\\

I am grateful to my colleagues who have been helping me a lot at Computational Vision Group. I would like say thanks to Dr. Ian Bland and Dr. Anthony Worrall who provide Grid Computing facilities so that I can finish my experiment in a limited time. I would like to thank Marc Bartel for encouraging me to continue my research. I would like to thank Dr. David Tweed and Longzhen Li for some technical discussion. I would like to thank Murray Evans and Dr. David Thirde for introducing STL and OOL in C++ to me. Also, I want to say thanks to Nicholas Carter, Saad Choudri, Anna Ellis, Dave Young, Mark Borg, Chen Qin, Hongwen Xu, Dr. Nils Siebel and Dr. Roberto Fraile for your kind help. I would like to thank all the individuals in computer vision and pattern recognition community for giving me help. I would like to thank Professor Mark Nixon for giving me an opportunity to attend \textit{FG2006}. I would like to thank Dr. Xiaojun Wu for providing me the \mbox{XM2VTS} face database. Also I would like to give my thank to Professor Haizhou AI, Professor Weiming Hu, Professor Steve Maybank and Professor Yunhong Wang for useful discussion and suggestion. I also would like to thank George Scott for proof reading my thesis.\\

Finally, I would like to thank my wife Mrs. Jing Jin Zhu, my parents and all other family members for all your love, understanding, support and encouragement.}


\newpage
\thispagestyle{empty}
\begin{center}
 \vspace*{2cm}
 Dedicated to my parents
\end{center}